\subsection{REPORTING A PROBLEM}

STRUCTURE:
\begin{enumerate}
\item Greeting
\item Starting your purpose: reporting a problem
\item Giving details
\item Calling to Action
\item Closing
\end{enumerate}
%--------------------------------------------------------------------
\subsubsection{Starting your purpose}
\begin{itemize}
\item I am writing to inform you that...
\item Lately we've encountered a problem with...
\item There is an issue with...
\item I am having an issue with...
\item I have trouble with...
\item I am facing a problem...
\end{itemize}
%--------------------------------------------------------------------
\subsubsection{Giving details}
\begin{itemize}
\item I had difficulty with...
\item The only problem is that...
\item I have tried unsuccessfully to resolve this...
\item The security problems have been identified...
\item The problem first arose in...
\item The problem lies in lack of...
\item This illustrates another potential problem.
\item This caused us considerable inconvenience.
\end{itemize}
%--------------------------------------------------------------------
\subsubsection{Calling to Action}
\subparagraph{Formal}
\begin{itemize}
\item I would like to seek your assistance with...
\item I would appreciate it if you could assist with...
\item I would be very grateful if you could offer me...
\item I would appreciate your assistance in...
\item I am looking forward to your feedback at your earliest convenience.
\end{itemize}

\subparagraph{Neutral}
\begin{itemize}
\item Shall we use...
\item Please let me know...
\item Can I ask you to look into the matter with...
\item I really need your help with...
\item Could you, please, confirm whether you find it acceptable?
\item Can I ask you to look into the matter with ..?
\end{itemize}

\paragraph{Setting a deadline}

\subparagraph{Formal}
\begin{itemize}
\item I would appreciate it if you replied by...
\item I look forward to receiving a reply at your earliest convenience.
\item I would be grateful if you could respond within 2 days.
\end{itemize}

\subparagraph{Neutral}
\begin{itemize}
\item I need your response by/before...
\item Hope to hear from you by...
\end{itemize}
%--------------------------------------------------------------------
\subsubsection{Closing line}
\begin{itemize}
\item Thanks in advance for your help/assistance.
\item Thank you for your cooperation in this matter.
\end{itemize}
%--------------------------------------------------------------------
\subsubsection{Synonyms}
\subparagraph{Problem:}
\begin{itemize}
\item Complication
\item Issue
\item Obstacle
\item Question
\item Trouble
\item Disagreement
\item Doubt
\item Bug
\item Hitch
\item Inconvenience
\item Breakdown
\item Computer
\item Malfunction
\item Defect
\item Error
\item Failure
\item Fault
\item Something wrong
\item Incident
\item Delay
\item Concern
\end{itemize}
 
\subparagraph{Problematic:}
\begin{itemize}
\item Questionable
\item Tricky
\item Uncertain
\item Unsettled
\item Arguable
\item Unclear
\item Undecided
\item Unpredictable
\item Complicated
\end{itemize}
