\subsection{DEALING WITH A PROBLEM}

STRUCTURE:
\begin{enumerate}
\item Greeting
\item Showing empathy/apologizing/thanking for feedback
\item Explaining why or ho the problem happened
\item Offering a solution
\item Inquiring if the solution is acceptable
\item Offering further help if necessary
\item Apologizing/thanking for feedback
\item Closing
\end{enumerate}
%--------------------------------------------------------------------
\subsubsection{Showing empathy/apologizing/thanking for feedback}
\subparagraph{Formal}
\begin{itemize}
\item Please allow me to apologize for...
\item Please accept our/my (sincere) apologies for...
\end{itemize}

\subparagraph{Neutral}
\begin{itemize}
\item I'm sorry to hear that...
\item I am really sorry for the delay in...
\item I realize how complicated it is to...
\item I can understand how frustrating it is when your Widget breaks down.
\item I know how confusing it must be when...
\item I understand that it would be very handy to...
\item I'm glad you reported the problem so that we can take care of this right away.
\end{itemize}

\paragraph{Appreciation of feedback}
\subparagraph{Formal}
\begin{itemize}
\item Thanks for the update.
\item Thanks for pointing out these issues.
\item Thank you for drawing our attention to the issue with...
\item Thank you for your feedback on...
\item I appreciate the opportunity to clarify what we think has happened.
\end{itemize}

\subparagraph{Neutral}
\begin{itemize}
\item We do appreciate your informing us about...
\end{itemize}

%--------------------------------------------------------------------
\subsubsection{Explaining why or ho the problem happened}
\begin{itemize}
\item I have looked into your question.
\item I have investigated the issue.
\item The investigation revealed...
\item After studying ..., it was found that...
\end{itemize}

%--------------------------------------------------------------------
\subsubsection{Offering a solution}
\subparagraph{Formal}
\begin{itemize}
\item I would be delighted to assist you.
\item In compensate for the inconvenience caused we would like to offer you...
\end{itemize}

\subparagraph{Neutral}
\begin{itemize}
\item I suggest that you (apply)...
\item I think it would be a good idea to...
\item I recommend that you (apply)...
\item Me second suggestion is that...
\item You should try to apply...
\item In order to respond to this issue, we will... This will not happen again.
\end{itemize}

%--------------------------------------------------------------------
\subsubsection{Inquiring if the solution is acceptable}
\subparagraph{Formal}
\begin{itemize}
\item Could you let me know whether the steps described are acceptable for you?
\end{itemize}

\subparagraph{Neutral}
\begin{itemize}
\item Can you confirm that the offered timing is OK for you?
\item Please let me know if it helped to sort out the issue.
\item I'm glad you reported the problem so that we can take care of this right away.
\end{itemize}

%--------------------------------------------------------------------
\subsubsection{Offering further help if necessary}
\subparagraph{Formal}
\begin{itemize}
\item Should you have any further queries/questions, do not hesitate to contact me.
\end{itemize}

\subparagraph{Neutral}
\begin{itemize}
\item Let me know if you need anything else.
\item Feel free to contact me, if you have further questions.
\end{itemize}

%--------------------------------------------------------------------
\subsubsection{Apologizing}
\begin{itemize}
\item Once again, sorry for the inconvenience caused.
\item Once again, I am really sorry for...
\item Once again, I do apologies for...
\item Please accept my apologies for the inconvenience caused.
\end{itemize}

%--------------------------------------------------------------------
\subsubsection{Thanking for feedback}
\begin{itemize}
\item Thank you for bringing this problem/matter to my attention.
\item I really appreciate your valuable feedback.
\end{itemize}
